---
title: "Week 10 - Section 2"
author: "Andrea Fox"
date: "10/30/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(devtools)
library(tidyverse)
library(dplyr)
library(tidyr)
```

# Section 2 – Week 10 – Cleaning Your Data and Exploratory Data Analysis
*1. Data importing and cleaning steps are explained in the text and in the DataCamp exercises (tell me why you are doing the data cleaning activities that you perform) and follow a logical process.*

*2. With a clean dataset, show what the final data set looks like. However, do not print off a data frame with 200+ rows; show me the data in the most condensed form possible.*

*3. What do you not know how to do right now that you need to learn to import and cleanup your dataset?* 

# Data Source:
https://data.kcmo.org/Crime/KCPD-Crime-Data-2018/dmjw-d28i

##  1 Data Importing and Cleaning
```{r Data Clean}

setwd("C:/Users/Andrea Fox/OneDrive/Documents/R/DSC520 Statistics Using R")

#Import the raw data and create initial dataframe
kcpd.18 <- read.csv("KCPD_Crime_Data_2018.csv", header = TRUE)

#Looking at whether my data is a dataframe, checking column names, glimpsing data, and checking summary
class(kcpd.18)
dim(kcpd.18)
names(kcpd.18)
glimpse(kcpd.18)
summary(kcpd.18)

#Need to find out if I have an NAs
any(is.na(kcpd.18))
sum(is.na(kcpd.18))
summary(kcpd.18)
complete.cases(kcpd.18)

#There are quite a few NA's in my entire dataset. At this point I want to create a subset of the data to narrow down the NA problem.
names(kcpd.18)
myvars <- c('Report_No', 'Reported_Date', 'Reported_Time', 'Offense', 'Description', 'Zip.Code', 'Area', 'Firearm.Used.Flag')
main_kcpd18 <- kcpd.18[,myvars]
summary(main_kcpd18)

#Remove NA's from new dataset
na.omit(main_kcpd18)
summary(main_kcpd18)

#Offense only had codes while the Description column had the type of crime, but the data was all over the place. Going to unite into one column named crime.
main2_kcpd18 <- unite(main_kcpd18, Crime, Offense, Description)
```


## 2 Data Display

```{r Data Display}
head(main2_kcpd18)
```

## 3 What's next?

>I ran into a lot of problems when cleaning the data with the biggest of not knowing really where to start. I decided to go through Cleaning Data Using R on DataCamp to see if I could pick up a few things, which really helped me follow a list of ideas. I had an exceptionally hard time figuring out the correct way to create my main_kcpd18 dataset from the original. It kept telling me I had an undefined column. Turns out I had originally combined Offense and Description before creating the subset and it didn't recognize Crime. So I deleted that out and moved it underneath creating another dataset of main2_kcpd18. For now this looks to be the bulk of what I'm going to work with to answer the majority of my questions.

>Things I don't know as of yet:
>Will I use the other columns like Age or Sex?
>Did I clean everything or will I experience issues?
>I tried looking at outliers, but most of my data is not numerical, so not sure if that will be an issue here



